---
title: "Tripadvisor"
author: "Sheetal & Sampoorna"
date: "3/8/2018"
output: html_document
---


HI All, the Aim over here is to scrap the details from the trip advisor page.
Lets start withe step one loading the rvest libraries and opening the link for GOA hotesl for dae MAy 1 -May 5
```{r setup, include=FALSE}
library("rvest")
library("XML")
# IMDB Top 250 Movies
url = "https://www.tripadvisor.in/Hotels-g297604-Goa-Hotels.html"
page = read_html(url)

page
```

## R Markdown

Now the tag Prominent is storing the Hotel Name and link for the hotel search and details . We got to know this from CSS selector tool. So lets copy the Node details and check for the Node 1 in which format the data is stored.

```{r cars}

hotel.nodes = html_nodes(page,'.prominent')
# Check one node
xmlTreeParse(hotel.nodes[[1]])
#hotel.nodes[[1]]
```

From the above we can see that hotel Name is stored in the Node and link details is stored in the tag a and node href.
So am copying the link and appending it to https://www.tripadvisor.in


```{r pressure, echo=FALSE}
hotel.link = sapply(html_attrs(hotel.nodes),`[[`,'href')
hotel.link = paste0("https://www.tripadvisor.in",hotel.link)

hotel.name = html_text(hotel.nodes)

```

We now have the hotel names lets take it to next step and find the price of the room and amount we are saving on it.
from CSS selector we found that the price is present on the node ".save.autoResize.ui_column.is-hidden-mobile" and saved ammount is present on the node ".price.autoResize".

Found only 22 rows for save amount so adding extra 8 zeros in it.

```{r}
save.node = html_nodes(page,'.save.autoResize.ui_column.is-hidden-mobile')
 
price.node = html_nodes(page,'.price.autoResize')
# Check one node

Save_amount = html_text(save.node)
price = html_text(price.node)
price= iconv(price, 'utf-8', 'ascii', sub='') 
Save_amount= iconv(Save_amount, 'utf-8', 'ascii', sub='') 
 Save_amount=gsub('SAVE ','',Save_amount)
```


```{r}
if (length(Save_amount)!=30)
{
  for ( i in length(Save_amount):30){
    Save_amount[i]=0
  }
}
```

Lets scrap in further more.
Lets open each hotel link find out the rating, number of reviews,address and Facility.
Rating and NUmber of review are present on same NOde -".rating"
address is on  ".map-pin-fill"" 
Facility is on ".highlightedAmenity" ( the data is recievied in list for which i have converted into comma seprated string.)




```{r}

rating_hotel=vector('character')
review=vector('character')
facility=vector('character')
address=vector('character')

for ( i in 1:length(hotel.link))
{
details = hotel.link[i]
details_page = read_html(details)

# Check one node
##xmlTreeParse(price.nodes[[1]])

rating.nodes = html_nodes(details_page,'.rating ') %>%
  html_text()

##

rating= trimws(gsub('reviews',' ', rating.nodes))

rating_review=tryCatch(strsplit(rating,' ')[[2]],
           error = function(e) print(0))

##print(rating_review)
review[i]=tryCatch(rating_review[2],
           error = function(e) print(0))
rating_hotel[i]=tryCatch(rating_review[1],
           error = function(e) print(0))


  address.nodes = html_nodes(details_page,'.map-pin-fill ') %>%
           html_text() 
  
  address[i]=gsub('See on map','',address.nodes[2])
    

facility.node = html_nodes(details_page,'.highlightedAmenity')
 facility_list= tryCatch( html_text(facility.node)  ,
                      error=function(e) print (0))
 facility_str=facility_list[1]
 for ( j in 2:length(facility_list)){
   facility_str=paste0(facility_str,',',facility_list[j])
 }
 
facility[i]=facility_str

}
```


Adding up all the columns and converting it into a dataframe.


```{r}
besthotel = data.frame(hotel.name,  hotel.link,rating_hotel,price,Save_amount,review,facility,address)
besthotel
```


Here is the way you could scrape data from tripadvisor. if you need for different city or time, please change the data and copy the link here in URL variable.


